Assessing Lime

### 2019-09-13 journals/04-assessing_lime/04-assessing_lime.Rmd
updated theme of journal 04

---
title: "Assessing Lime"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---

>>>>

---
title: "Assessing Lime"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    theme: cerulean
    highlight: textmate
---
